A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
Adding bibliography

The survey data allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
How quickly is work completed in a given language? 
Are crowdsourced translations reliably good? 
How often do workers misrepresented their language abilities to falsely obtain financial rewards?

@@

\section{Related Work}
Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis (Snow et al.). More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks (CCB).

@@

As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population. Early demographic studies by Ipeirotis revealed that Turkers are typically younger and more educated than the population as a whole. The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation. A follow-up study by Ross et al. found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers. Ross et al. also suggested that the international presence on MTurk has been growing over time. While there has not yet been a thorough investigation of Turkers' language abilities, Munro compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu). No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

@@

Also, with intelligent quality control techniques, MTurk can prove that $P = NP$, solve the problems in the Middle East, and allow you to eat carbs and still lose weight.

%\begin{thebibliography}{}

%\bibitem[\protect\citename{}yrs]{name}
%name
%\newblock year
%\newblock title
%\newblock In {\em journal}.

%\end{thebibliography}

>>>>

Surveying thousands of workers allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
How quickly is work completed in a given language? 
Are crowdsourced translations reliably good? 
How often do workers misrepresented their language abilities to 
%falsely
obtain financial rewards?

@@

\section{Related Work}
Crowdsourced data has been used in a variety of machine learning applications, including computer vision (Sorokin et al.), paraphrasing (Nakov et al.) and sentiment analysis \cite{Snow2008}. More recently, in 2010, NAACL hosted a workshop on Creating Speech and Language Data with MTurk, in which MTurk was used to generate data for 24 different natural language tasks \cite{callisonburch-dredze:2010:MTURK}.

@@

As the use of MTurk has grown, researchers have become interested in who exactly makes up the Turker population. Early demographic studies by \newcite{ipeirotis:2010:demographics} revealed that Turkers are typically younger and more educated than the population as a whole. The study found that while most Turkers cite money as a motivation for working on MTurk, few cite it as their only motivation. A follow-up study by Ross et al. found that the majority of Turkers were located in the US, 30\% of Turkers were located in India, and that Indian Turkers tend to have lower incomes than US-based Turkers. Ross et al. also suggested that the international presence on MTurk has been growing over time. While there has not yet been a thorough investigation of Turkers' language abilities, Munro compiled survey responses of 2,000 Turkers, revealing that four of the six most represented languages come from India (the top six being Hindi, Malayalam, Tamil, Spanish, French, and Telugu). No study has yet been conducted to comprehensively assess the language skills of the growing number of international and bilingual Turkers or to analyze the potential of MTurk to support work in low-resource languages.

@@

\bibliographystyle{acl2012}
\bibliography{mturk}
